Demers Cartogram with Rivers

### 2023-04-20 paper/section/main.tex
draft: e_t percentage

\bobgraph{Node Layout and Overlap Removal:} We first apply the Fast Node Overlap Removal (FNOR) algorithm that solves the Variable Placement with Separation Constraints (VPSC) problem \cite{dwyer2006Fast} in order to remove overlap between square nodes. We chose FNOR over other node overlap removal algorithms because FNOR is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. Initialized with a pixel size of unity, we gradually increase the node size by one unit at a time to ensure smooth transitions. An increase in $ \nodeSize $ can cause the nodes to overlap. During overlap removal, we compute node trajectories (See \Cref{alg:TranslateNode}) and translate nodes to their new position. Nodes that cross a river, denoted $ \NxR $, are translated back to their previous position. If a node oscillates across a river, we identify this as a stalemate. One iteration of the layout ends when 1) no node overlap is present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one unit and repeat the algorithm until the average cartographic error, $ nodeCartographicError $, a measure set by the user, reaches its maximum value $ nodeCartographicErrorMax $. The gradual size increase process provides stability to the layout and helps minimize geographical error.

@@

{
\begin{figure*}[tb!]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{figure/UI.png}
    \caption{A screenshot of the software. User options are provided to adjust the terminating conditions (size and error), color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static or dynamic. See \Cref{subsec:{User Options}} for more on user options. \new{In this figure, $ \nodeTopologicalError $ is reduced from 13 to 0, and $ \nodeCartographicError $ for X and Y axes are 59.5 and 56.56, respectively. }}
    \label{fig:overview}
\end{figure*}
}

>>>>

\bobgraph{Node Layout and Overlap Removal:} We first apply the Fast Node Overlap Removal (FNOR) algorithm that solves the Variable Placement with Separation Constraints (VPSC) problem \cite{dwyer2006Fast} in order to remove overlap between square nodes. We chose FNOR over other node overlap removal algorithms because FNOR is able to provide spread minimization and node movement minimization while maintaining a good level of global shape preservation \cite{chen2020Node}. Initialized with a pixel size of unity, we gradually increase the node size by one unit at a time to ensure smooth transitions. An increase in $ \nodeSize $ can cause the nodes to overlap. During overlap removal, we compute node trajectories (See \Cref{alg:TranslateNode}) and translate nodes to their new position. Nodes that cross a river, denoted $ \NxR $, are translated back to their previous position. If a node oscillates across a river, we identify this as a stalemate. One iteration of the layout ends when 1) no node overlap is present; 2) no nodes cross a river. We then increase $ \nodeSize $ by one unit and repeat the algorithm until the average cartographic error, $ \nodeCartographicError $, a measure set by the user, reaches its maximum value $ \nodeCartographicErrorMax $. The gradual size increase process provides stability to the layout.

@@

{
\begin{figure*}[tb!]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio]{figure/UI.png}
    \caption{A screenshot of the user interface. User options are provided to adjust the terminating conditions (size and error), color mapping, visibility of nodes and rivers. Other options include the ability to control the overlap removal behavior: rivers can be static or dynamic. See \Cref{subsec:{User Options}} for more on user options. In this figure, an $ \nodeTopologicalError $ of 9.63\% is eliminated.}
    \label{fig:overview}
\end{figure*}
}
